Age-related changes in plant growth and traits

### 2015-08-19 results_growth.Rmd
Attempt at simplifying color and label selection

source("scripts/summary_dataframes.R")
source("scripts/functions.R")
```
#Growth data, general patterns
- proportion of maxH matters more for some species than others. 
    1. The 4 "canopy" species all tend to have high correlations between "prop maxH" and growth and reproductive investment (both relative and absolute)  (HATE, BAER, PELA, PEPU)
    2. The lower-growing species are more variable, with "prop maxH"" mattering more for some than others - not surprising since some species like BOLE, PILI show inconsistent increases in H with increasing age, due to breakage, shedding

@@

###Weight vs. height
- No surprises here , but need to fit proper lines to the data (**CURVE FITTING**)
- Plants asymptote in weight as they reach their maximum height. This is true for all species, although some species, like BOLE and GRBU, have a much messier scatter than others  
- The follow on of course is to look at growth measures vs. height   
- NOTE: The variable "prop_maxH" is "current height/maximum species height (across all sites)", hence varying from 0-1. This lets data from all species to be plotted together  
```{r, echo=FALSE, message=FALSE, fig.width=7, fig.height=7}
par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.6,0.2))
plot((total_weight~prop_maxH), SummaryInd, col=col.spp[as.factor(species)],pch=16,log="y")
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
```

@@

```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(.8,0.3,.5,0.2), mai=c(.7,1,.1,0.2))
plot((growth_inv~prop_maxH), SummaryInd, log="y", col=col.spp[as.factor(species)],pch=16,xlab="")
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

plot(growth_inv~prop_maxH, SummaryInd, log="y", col=col.age[as.factor(age)],pch=16,ylab="",xlab="")
legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
mtext("proportion Hmax", 1, outer=TRUE,cex=1.2)
```

@@

```{r, echo=FALSE, message=FALSE, fig.width=7, fig.height=7}
par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
plot(RGR~prop_maxH,SummaryInd,col=col.spp[as.factor(species)],pch=16)
legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
```

@@

```{r, echo=FALSE,message=FALSE, fig.width=14, fig.height=7}
par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
plot(growth_shoot_area~growth_stem_area,data=subset(SummaryInd), log="xy",col=col.spp[as.factor(species)], pch=16, cex=.8,xlab="change in basal stem area",ylab="change in shoot area")
legend("bottomright",col=col.spp, legend=names(labels.spp), pch=16, cex=1,bty="n")

@@

```{r, echo=FALSE,message=FALSE, fig.width=7, fig.height=7}
par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
plot(shoot_leaf_count~age,data=subset(SummaryInd,age>2),log="xy", xlab="age",ylab="final leaf count along shoot",col=col.spp[as.factor(species)])
legend("bottomright",col=col.spp, legend=names(labels.spp), pch=16, cex=1,bty="n")

@@

```{r, echo=FALSE,message=FALSE,, fig.width=7, fig.height=7}
par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
plot(leaf_weight~total_weight,SummaryInd, log="xy",col=col.spp[as.factor(species)], pch=16, cex=0.8)
legend("bottomright",col=col.spp, legend=names(labels.spp), pch=16, cex=.8, bty="n")
```

@@

```{r, echo=FALSE,message=FALSE,, fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
mod <- lm(prop_maxH~growth_shoot_length,data=subset(SummaryInd,age>2))
plot(growth_shoot_length~prop_maxH,data=subset(SummaryInd,age>2),log="y", ylab="shoot extension (mm)",col=col.spp[as.factor(species)],pch=16)
legend(12,200,col=col.spp, legend=names(labels.spp), pch=16, cex=.8,bty="n")
words.bottom.right.logy(mod)

mod <- lm(age~species*growth_shoot_length,data=subset(SummaryInd,age>2))
plot(growth_shoot_length~age,data=subset(SummaryInd,age>2),log="xy", ylab="shoot extension (mm)",col=col.spp[as.factor(species)],pch=16)
words.bottom.right.logxy(mod)
anova(mod)

@@

###Diameter increase in shoots vs. whole plant
- The slope of the relationship lessens with age  
- There is quite a bit of noise in the relationship  
- However, in many cases, older plants show less of a change in shoot diameter for a given change in basal diameter; the opposite pattern as is predicted if ever fewer shoots are sustaining growth  
- Instead, each shoot matters ever less to the overall increase in basal area in larger plants
- NOTE: Plots not correct right now - wrong number of points in some and definitely wrong coloring by age
```{r, echo=FALSE,message=FALSE}
par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
mod <- lm (growth_shoot_area ~ growth_stem_area*species*age,data=subset(SummaryInd, age>1.4))
plot((growth_shoot_area/10000) ~ growth_stem_area,data=subset(SummaryInd, age>1.4), log="xy",col=col.age2[as.factor(age)], pch=16)
abline(0,1)
words.bottom.right.logxy(mod)
legend("topleft",col=col.age, labels.age, pch=16, cex=1, bty="n")
anova(mod)
```

@@

legend("topleft",col=col.age2, labels.age2, pch=16, cex=1, bty="n")
mtext("growth in basal stem area", 1, outer=TRUE,cex=1.2)
mtext("growth in leader stem area", 2, outer=TRUE,cex=1.2)
```

### Leaf area versus plant size and height
```{r, echo=FALSE, message=FALSE, fig.width=14, fig.height=14}
par(mfrow=c(2,2), cex=1, omi=c(.1,.2,.1,.1), mai=c(1,1,.5,0.2)) 
plot(leaf_area~total_weight, SummaryInd,log="xy",col=col.age[as.factor(age)], pch=16)
mod <- lm(log(total_weight)~log(leaf_area), SummaryInd)
words.bottom.right.logxy(mod)

plot(leaf_area~prop_maxH, SummaryInd,log="y",col=col.age[as.factor(age)], pch=16)

plot(leaf_area~total_weight, SummaryInd,log="xy",col=col.spp[as.factor(species)], pch=16)
words.bottom.right.logxy(mod)

plot(leaf_area~prop_maxH, SummaryInd,log="y",col=col.spp[as.factor(species)], pch=16)
```

### Leaf weight versus plant size and height
* One of the things I find most interesting here is how different clusters of species follow different trajectories (4th graph)  
* BAER, HATE, PELA, and PEPU have similar curves to one another; then comes a band with GRBU and GRSP, followed by all other species except PILI  
* oldest plants (&PILI) fall below the main line of points  
```{r, echo=FALSE, message=FALSE, fig.width=14, fig.height=14}
par(mfrow=c(2,2), cex=1, omi=c(.1,.2,.1,.1), mai=c(1,1,.5,0.2)) 
plot(leaf_weight~total_weight, SummaryInd,log="xy",col=col.age[as.factor(age)], pch=16)
mod <- lm(log(total_weight)~log(leaf_weight), SummaryInd)
words.bottom.right.logxy(mod)

plot(leaf_weight~prop_maxH, SummaryInd,log="y",col=col.age[as.factor(age)], pch=16)

plot(leaf_weight~total_weight, SummaryInd,log="xy",col=col.spp[as.factor(species)], pch=16)
words.bottom.right.logxy(mod)

plot(leaf_weight~prop_maxH, SummaryInd,log="y",col=col.spp[as.factor(species)], pch=16)
```

@@

par(mfrow=c(2,2), cex=1, omi=c(.1,.2,.1,.1), mai=c(1,1,.5,0.2)) 
plot((RGR_leaf)~(RGR_stem), SummaryInd,col=col.age[as.factor(age)], pch=16,ylim=c(-1,4))
abline(0,0)
abline(0,1)
legend("topleft",col=col.age, labels.age, pch=16, cex=1, bty="n")

plot((leaf_area)~(stem_weight), SummaryInd,col=col.age[as.factor(age)], pch=16,log="xy")
abline(0,1)
text(1000,1800,srt=39,labels="1:1 line")

plot((RGR_leaf)~(RGR_stem), SummaryInd,col=col.spp[as.factor(species)], pch=16,ylim=c(-1,4),xlab="")
abline(0,0)
abline(0,1)
legend("topleft",col=col.spp, legend=names(labels.spp), pch=16, cex=.9, bty="n")

plot((leaf_area)~(stem_weight), SummaryInd,col=col.spp[as.factor(species)], pch=16,log="xy",xlab="")
abline(0,1)
text(1000,1800,srt=39,labels="1:1 line")
words.bottom.right.logxy(mod)
```

@@

### Species with larger seeds have higher growth rates  
- The same basic relationship exists across all ages, so combined all data here  
```{r, echo=FALSE,message=FALSE, fig.width=7, fig.height=7}
par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
plot(growth_inv_mean ~ seed_size,data=subset(SummarySppAge,age>.5),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="seed size (mg)",ylab="growth investment (mg per year)",main="Effect of seed size on growth rates")
legend("topleft",col=col.age, labels.age, pch=16, cex=1,bty="n")
text(growth_inv_mean ~ seed_size, data=subset(SummarySppAge,age==9), labels=species, pos=2, offset=-2.4, cex=0.9,col="blue")
```

### Species with greater maximum height have higher growth rates
- For younger plants there is no relationship with *SPECIES* overall maximum H  
- There is a positive correlation with the maximum height the species reaches at a given age -i.e. fast growing young plants are tall when young.  
```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
plot(growth_inv_mean ~ maxH,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Seedlings")
text(growth_inv_mean ~ maxH, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
mod <- lm(growth_inv_mean ~ maxH, data=subset(SummarySppAge,age==1.4))
words.bottom.right.logxy(mod)

@@

plot(growth_inv_mean ~ maxH,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Adults")
text(growth_inv_mean ~ maxH, data=subset(SummarySppAge,age==5), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
mod <- lm(growth_inv_mean ~ maxH, data=subset(SummarySppAge,age>3))
words.bottom.right.logxy(mod)
legend("topleft",col=col.age,labels.age,pch=16, bty="n")

@@

### Species with higher wood density have lower growth rates  
- Adult plants strongly show this pattern
- However there is no relationship in younger plants  
```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
plot(growth_inv_mean ~ WD_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Seedlings")
text(growth_inv_mean ~ WD_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
mod <- lm(growth_inv_mean ~ WD_mean, data=subset(SummarySppAge,age==1.4))
words.bottom.left.logxy(mod)

plot(growth_inv_mean ~ WD_mean,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
text(growth_inv_mean ~ WD_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
mod <- lm(growth_inv_mean ~ WD_mean, data=subset(SummarySppAge,age==2.4))
words.bottom.left.logxy(mod)
legend("topright",col=col.age,labels.age,pch=16, bty="n")

plot(growth_inv_mean ~ WD_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Adults")
text(growth_inv_mean ~ WD_mean, data=subset(SummarySppAge,age==5), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
mod <- lm(growth_inv_mean ~ WD_mean, data=subset(SummarySppAge,age>3))
words.bottom.left.logxy(mod)

@@

* same wood density data plotted against RGR instead - also no pattern with young
```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
plot(RGR_mean ~ WD_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Seedlings")
text(RGR_mean ~ WD_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
mod <- lm(RGR_mean ~ WD_mean, data=subset(SummarySppAge,age==1.4))
words.bottom.right.logxy(mod)

plot(RGR_mean ~ WD_mean,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
text(RGR_mean ~ WD_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
mod <- lm(RGR_mean ~ WD_mean, data=subset(SummarySppAge,age==2.4))
words.bottom.right.logxy(mod)
legend("topright",col=col.age,labels.age,pch=16, bty="n")

@@

### Leaf area vs growth investment
```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
plot(growth_inv_mean ~ leaf_area_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Seedlings",ylim=c(100,50000))
text(growth_inv_mean ~ leaf_area_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
mod <- lm(growth_inv_mean ~ leaf_area_mean, data=subset(SummarySppAge,age==1.4))
words.bottom.right.logxy(mod)

@@

plot(growth_inv_mean ~ leaf_area_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Adults",ylim=c(100,1000000))
text(growth_inv_mean ~ leaf_area_mean, data=subset(SummarySppAge,age==7), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
mod <- lm(growth_inv_mean ~ leaf_area_mean, data=subset(SummarySppAge,age>3))
words.bottom.right.logxy(mod)
legend("topleft",col=col.age,labels.age,pch=16, bty="n")

@@

### Species with higher LMA have higher growth rates  
- This pattern is true for adult plants  
- But there is no relationship in seedlings (age=1.4) or saplings (age=2.4)  
- This is not predicted by Daniel's model or Anais' review; re-runing with RGR yields same results
- But relationship in adults disappears when HATE is removed...
```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
plot(growth_inv_mean ~ LMA_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Seedlings")
text(growth_inv_mean ~ LMA_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
mod <- lm(growth_inv_mean ~ LMA_mean, data=subset(SummarySppAge,age==1.4))
words.bottom.right.logxy(mod)

plot(growth_inv_mean ~ LMA_mean,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
text(growth_inv_mean ~ LMA_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
mod <- lm(growth_inv_mean ~ LMA_mean, data=subset(SummarySppAge,age==2.4))
words.bottom.right.logxy(mod)
legend("topright",col=col.age,labels.age,pch=16, bty="n")

>>>>

source("scripts/functions.R")
```
#Growth data, general patterns
- proportion of maxH matters more for some species than others. 
    1. The 4 "canopy" species all tend to have high correlations between "prop maxH" and growth and reproductive investment (both relative and absolute)  (HATE, BAER, PELA, PEPU)
    2. The lower-growing species are more variable, with "prop maxH"" mattering more for some than others - not surprising since some species like BOLE, PILI show inconsistent increases in H with increasing age, due to breakage, shedding

@@

###Weight vs. height
- No surprises here , but need to fit proper lines to the data (**CURVE FITTING**)
- Plants asymptote in weight as they reach their maximum height. This is true for all species, although some species, like BOLE and GRBU, have a much messier scatter than others  
- The follow on of course is to look at growth measures vs. height   
- NOTE: The variable "prop_maxH" is "current height/maximum species height (across all sites)", hence varying from 0-1. This lets data from all species to be plotted together  
```{r, echo=FALSE, message=FALSE, fig.width=7, fig.height=7}
par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.6,0.2))
plot((total_weight~prop_maxH), SummaryInd, col=col.spp(species),pch=16,log="y")
legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
```

@@

```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(.8,0.3,.5,0.2), mai=c(.7,1,.1,0.2))
plot((growth_inv~prop_maxH), SummaryInd, log="y", col=col.spp(species),pch=16,xlab="")
legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")

plot(growth_inv~prop_maxH, SummaryInd, log="y", col=col.age(age),pch=16,ylab="",xlab="")
legend("topleft",legend=labels.age(),col=col.age,pch=16, cex=.8,bty="n")
mtext("proportion Hmax", 1, outer=TRUE,cex=1.2)
```

@@

```{r, echo=FALSE, message=FALSE, fig.width=7, fig.height=7}
par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
plot(RGR~prop_maxH,SummaryInd,col=col.spp(species),pch=16)
legend("topright",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
```

@@

```{r, echo=FALSE,message=FALSE, fig.width=14, fig.height=7}
par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
plot(growth_shoot_area~growth_stem_area,data=subset(SummaryInd), log="xy",col=col.spp(species), pch=16, cex=.8,xlab="change in basal stem area",ylab="change in shoot area")
legend("bottomright",col=col.spp, legend=labels.spp(), pch=16, cex=1,bty="n")

@@

```{r, echo=FALSE,message=FALSE, fig.width=7, fig.height=7}
par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
plot(shoot_leaf_count~age,data=subset(SummaryInd,age>2),log="xy", xlab="age",ylab="final leaf count along shoot",col=col.spp(species))
legend("bottomright",col=col.spp, legend=labels.spp(), pch=16, cex=1,bty="n")

@@

```{r, echo=FALSE,message=FALSE,, fig.width=7, fig.height=7}
par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
plot(leaf_weight~total_weight,SummaryInd, log="xy",col=col.spp(species), pch=16, cex=0.8)
legend("bottomright",col=col.spp, legend=labels.spp(), pch=16, cex=.8, bty="n")
```

@@

```{r, echo=FALSE,message=FALSE,, fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
mod <- lm(prop_maxH~growth_shoot_length,data=subset(SummaryInd,age>2))
plot(growth_shoot_length~prop_maxH,data=subset(SummaryInd,age>2),log="y", ylab="shoot extension (mm)",col=col.spp(species),pch=16)
legend(12,200,col=col.spp, legend=labels.spp(), pch=16, cex=.8,bty="n")
words.bottom.right.logy(mod)

mod <- lm(age~species*growth_shoot_length,data=subset(SummaryInd,age>2))
plot(growth_shoot_length~age,data=subset(SummaryInd,age>2),log="xy", ylab="shoot extension (mm)",col=col.spp(species),pch=16)
words.bottom.right.logxy(mod)
anova(mod)

@@

###Diameter increase in shoots vs. whole plant
- The slope of the relationship lessens with age  
- There is quite a bit of noise in the relationship  
- However, in many cases, older plants show less of a change in shoot diameter for a given change in basal diameter; the opposite pattern as is predicted if ever fewer shoots are sustaining growth  
- Instead, each shoot matters ever less to the overall increase in basal area in larger plants
- NOTE: Plots not correct right now - wrong number of points in some and definitely wrong coloring by age
```{r, echo=FALSE,message=FALSE}
par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
mod <- lm (growth_shoot_area ~ growth_stem_area*species*age,data=subset(SummaryInd, age>1.4))
plot((growth_shoot_area/10000) ~ growth_stem_area,data=subset(SummaryInd, age>1.4), log="xy",col=col.age(age), pch=16)
abline(0,1)
words.bottom.right.logxy(mod)
legend("topleft",col=col.age, labels.age(), pch=16, cex=1, bty="n")
anova(mod)
```

@@

legend("topleft",col=col.age, labels.age(), pch=16, cex=1, bty="n")
mtext("growth in basal stem area", 1, outer=TRUE,cex=1.2)
mtext("growth in leader stem area", 2, outer=TRUE,cex=1.2)
```

### Leaf area versus plant size and height
```{r, echo=FALSE, message=FALSE, fig.width=14, fig.height=14}
par(mfrow=c(2,2), cex=1, omi=c(.1,.2,.1,.1), mai=c(1,1,.5,0.2)) 
plot(leaf_area~total_weight, SummaryInd,log="xy",col=col.age(age), pch=16)
mod <- lm(log(total_weight)~log(leaf_area), SummaryInd)
words.bottom.right.logxy(mod)

plot(leaf_area~prop_maxH, SummaryInd,log="y",col=col.age(age), pch=16)

plot(leaf_area~total_weight, SummaryInd,log="xy",col=col.spp(species), pch=16)
words.bottom.right.logxy(mod)

plot(leaf_area~prop_maxH, SummaryInd,log="y",col=col.spp(species), pch=16)
```

### Leaf weight versus plant size and height
* One of the things I find most interesting here is how different clusters of species follow different trajectories (4th graph)  
* BAER, HATE, PELA, and PEPU have similar curves to one another; then comes a band with GRBU and GRSP, followed by all other species except PILI  
* oldest plants (&PILI) fall below the main line of points  
```{r, echo=FALSE, message=FALSE, fig.width=14, fig.height=14}
par(mfrow=c(2,2), cex=1, omi=c(.1,.2,.1,.1), mai=c(1,1,.5,0.2)) 
plot(leaf_weight~total_weight, SummaryInd,log="xy",col=col.age(age), pch=16)
mod <- lm(log(total_weight)~log(leaf_weight), SummaryInd)
words.bottom.right.logxy(mod)

plot(leaf_weight~prop_maxH, SummaryInd,log="y",col=col.age(age), pch=16)

plot(leaf_weight~total_weight, SummaryInd,log="xy",col=col.spp(species), pch=16)
words.bottom.right.logxy(mod)

plot(leaf_weight~prop_maxH, SummaryInd,log="y",col=col.spp(species), pch=16)
```

@@

par(mfrow=c(2,2), cex=1, omi=c(.1,.2,.1,.1), mai=c(1,1,.5,0.2)) 
plot((RGR_leaf)~(RGR_stem), SummaryInd,col=col.age(age), pch=16,ylim=c(-1,4))
abline(0,0)
abline(0,1)
legend("topleft",col=col.age, labels.age(), pch=16, cex=1, bty="n")

plot((leaf_area)~(stem_weight), SummaryInd,col=col.age(age), pch=16,log="xy")
abline(0,1)
text(1000,1800,srt=39,labels="1:1 line")

plot((RGR_leaf)~(RGR_stem), SummaryInd,col=col.spp(species), pch=16,ylim=c(-1,4),xlab="")
abline(0,0)
abline(0,1)
legend("topleft",col=col.spp, legend=labels.spp(), pch=16, cex=.9, bty="n")

plot((leaf_area)~(stem_weight), SummaryInd,col=col.spp(species), pch=16,log="xy",xlab="")
abline(0,1)
text(1000,1800,srt=39,labels="1:1 line")
words.bottom.right.logxy(mod)
```

@@

### Species with larger seeds have higher growth rates  
- The same basic relationship exists across all ages, so combined all data here  
```{r, echo=FALSE,message=FALSE, fig.width=7, fig.height=7}
par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
plot(growth_inv_mean ~ seed_size,data=subset(SummarySppAge,age>.5),log="xy",col=col.age(age),pch=16,cex=1,xlab="seed size (mg)",ylab="growth investment (mg per year)",main="Effect of seed size on growth rates")
legend("topleft",col=col.age, labels.age(), pch=16, cex=1,bty="n")
text(growth_inv_mean ~ seed_size, data=subset(SummarySppAge,age==9), labels=species, pos=2, offset=-2.4, cex=0.9,col="blue")
```

### Species with greater maximum height have higher growth rates
- For younger plants there is no relationship with *SPECIES* overall maximum H  
- There is a positive correlation with the maximum height the species reaches at a given age -i.e. fast growing young plants are tall when young.  
```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
plot(growth_inv_mean ~ maxH,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Seedlings")
text(growth_inv_mean ~ maxH, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
mod <- lm(growth_inv_mean ~ maxH, data=subset(SummarySppAge,age==1.4))
words.bottom.right.logxy(mod)

@@

plot(growth_inv_mean ~ maxH,data=subset(SummarySppAge,age>3),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Adults")
text(growth_inv_mean ~ maxH, data=subset(SummarySppAge,age==5), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
mod <- lm(growth_inv_mean ~ maxH, data=subset(SummarySppAge,age>3))
words.bottom.right.logxy(mod)
legend("topleft",col=col.age,labels.age(),pch=16, bty="n")

@@

### Species with higher wood density have lower growth rates  
- Adult plants strongly show this pattern
- However there is no relationship in younger plants  
```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
plot(growth_inv_mean ~ WD_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Seedlings")
text(growth_inv_mean ~ WD_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
mod <- lm(growth_inv_mean ~ WD_mean, data=subset(SummarySppAge,age==1.4))
words.bottom.left.logxy(mod)

plot(growth_inv_mean ~ WD_mean,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
text(growth_inv_mean ~ WD_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
mod <- lm(growth_inv_mean ~ WD_mean, data=subset(SummarySppAge,age==2.4))
words.bottom.left.logxy(mod)
legend("topright",col=col.age,labels.age(),pch=16, bty="n")

plot(growth_inv_mean ~ WD_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Adults")
text(growth_inv_mean ~ WD_mean, data=subset(SummarySppAge,age==5), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
mod <- lm(growth_inv_mean ~ WD_mean, data=subset(SummarySppAge,age>3))
words.bottom.left.logxy(mod)

@@

* same wood density data plotted against RGR instead - also no pattern with young
```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
plot(RGR_mean ~ WD_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Seedlings")
text(RGR_mean ~ WD_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
mod <- lm(RGR_mean ~ WD_mean, data=subset(SummarySppAge,age==1.4))
words.bottom.right.logxy(mod)

plot(RGR_mean ~ WD_mean,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
text(RGR_mean ~ WD_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
mod <- lm(RGR_mean ~ WD_mean, data=subset(SummarySppAge,age==2.4))
words.bottom.right.logxy(mod)
legend("topright",col=col.age,labels.age(),pch=16, bty="n")

@@

### Leaf area vs growth investment
```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
plot(growth_inv_mean ~ leaf_area_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Seedlings",ylim=c(100,50000))
text(growth_inv_mean ~ leaf_area_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
mod <- lm(growth_inv_mean ~ leaf_area_mean, data=subset(SummarySppAge,age==1.4))
words.bottom.right.logxy(mod)

@@

plot(growth_inv_mean ~ leaf_area_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Adults",ylim=c(100,1000000))
text(growth_inv_mean ~ leaf_area_mean, data=subset(SummarySppAge,age==7), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
mod <- lm(growth_inv_mean ~ leaf_area_mean, data=subset(SummarySppAge,age>3))
words.bottom.right.logxy(mod)
legend("topleft",col=col.age,labels.age(),pch=16, bty="n")

@@

### Species with higher LMA have higher growth rates  
- This pattern is true for adult plants  
- But there is no relationship in seedlings (age=1.4) or saplings (age=2.4)  
- This is not predicted by Daniel's model or Anais' review; re-runing with RGR yields same results
- But relationship in adults disappears when HATE is removed...
```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
plot(growth_inv_mean ~ LMA_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Seedlings")
text(growth_inv_mean ~ LMA_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
mod <- lm(growth_inv_mean ~ LMA_mean, data=subset(SummarySppAge,age==1.4))
words.bottom.right.logxy(mod)

plot(growth_inv_mean ~ LMA_mean,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
text(growth_inv_mean ~ LMA_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
mod <- lm(growth_inv_mean ~ LMA_mean, data=subset(SummarySppAge,age==2.4))
words.bottom.right.logxy(mod)
legend("topright",col=col.age,labels.age(),pch=16, bty="n")
